Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-03-06 sections/observations.tex
Checked Observations section bc of weird merge.
Added Optical specs to Observations section

The livestream lightcurve was created by grayscaling the image of the eclipse and using Otsu thresholding to only count pixels above a certain value.

>>>>

The livestream of the solar eclipse was created using a Sony Alpha 6400 camera with a Sony FE 24mm-240mm f/3.5-6.3 lens and NiSi Solar Filter Pro Nan UV/IR Cut ND 100000 72mm filter.
This solar filter was removed during totality, marked by 2460409.2849 JD and 2460409.2884 JD.
This setup was attached to a Meade-14 LX200R on a Paramount MX+ equatorial mount for target tracking.
The lightcurve for this data was created by grayscaling the image of the eclipse and using Otsu thresholding to only count pixels above a certain value.
